\documentclass{article}
\usepackage{amsmath}
\usepackage{chemfig}

\title{Stoichiometry Problems 1: Basic Stoichiometry}
\author{}
\date{}

\begin{document}

\maketitle

\section*{Problems and Answers}

\begin{enumerate}
    \item How many moles of hydrogen gas are produced when 2 moles of zinc react with hydrochloric acid?
    \[
    \text{Zn} + 2\text{HCl} \rightarrow \text{ZnCl}_2 + \text{H}_2
    \]
    \textbf{Answer:} 1 mole of \(\text{H}_2\)

    \item Calculate the mass of water produced when 5 grams of hydrogen gas reacts with oxygen gas.
    \[
    2\text{H}_2 + \text{O}_2 \rightarrow 2\text{H}_2\text{O}
    \]
    \textbf{Answer:} 45 grams of \(\text{H}_2\text{O}\)

    \item Determine the number of moles of carbon dioxide produced when 10 grams of methane combusts completely.
    \[
    \text{CH}_4 + 2\text{O}_2 \rightarrow \text{CO}_2 + 2\text{H}_2\text{O}
    \]
    \textbf{Answer:} 0.625 moles of \(\text{CO}_2\)

    \item How many grams of sodium chloride are produced when 2 moles of sodium react with chlorine gas?
    \[
    2\text{Na} + \text{Cl}_2 \rightarrow 2\text{NaCl}
    \]
    \textbf{Answer:} 117 grams of \(\text{NaCl}\)

    \item Calculate the volume of oxygen gas required to completely react with 8 grams of methane at STP.
    \[
    \text{CH}_4 + 2\text{O}_2 \rightarrow \text{CO}_2 + 2\text{H}_2\text{O}
    \]
    \textbf{Answer:} 22.4 liters of \(\text{O}_2\)

    \item Determine the mass of iron(III) oxide produced when 10 grams of iron reacts with excess oxygen.
    \[
    4\text{Fe} + 3\text{O}_2 \rightarrow 2\text{Fe}_2\text{O}_3
    \]
    \textbf{Answer:} 14.3 grams of \(\text{Fe}_2\text{O}_3\)

    \item How many moles of ammonia are produced when 3 moles of nitrogen gas react with hydrogen gas?
    \[
    \text{N}_2 + 3\text{H}_2 \rightarrow 2\text{NH}_3
    \]
    \textbf{Answer:} 6 moles of \(\text{NH}_3\)

    \item Calculate the mass of carbon dioxide produced when 15 grams of ethane combusts completely.
    \[
    2\text{C}_2\text{H}_6 + 7\text{O}_2 \rightarrow 4\text{CO}_2 + 6\text{H}_2\text{O}
    \]
    \textbf{Answer:} 44 grams of \(\text{CO}_2\)

    \item Determine the number of moles of sulfur dioxide produced when 20 grams of sulfur reacts with oxygen gas.
    \[
    \text{S} + \text{O}_2 \rightarrow \text{SO}_2
    \]
    \textbf{Answer:} 0.625 moles of \(\text{SO}_2\)

    \item How many grams of calcium carbonate are produced when 5 moles of calcium oxide react with carbon dioxide?
    \[
    \text{CaO} + \text{CO}_2 \rightarrow \text{CaCO}_3
    \]
    \textbf{Answer:} 500 grams of \(\text{CaCO}_3\)

    \item Calculate the volume of hydrogen gas produced when 10 grams of aluminum reacts with hydrochloric acid at STP.
    \[
    2\text{Al} + 6\text{HCl} \rightarrow 2\text{AlCl}_3 + 3\text{H}_2
    \]
    \textbf{Answer:} 12.4 liters of \(\text{H}_2\)

    \item Determine the mass of sodium sulfate produced when 25 grams of sodium hydroxide reacts with sulfuric acid.
    \[
    2\text{NaOH} + \text{H}_2\text{SO}_4 \rightarrow \text{Na}_2\text{SO}_4 + 2\text{H}_2\text{O}
    \]
    \textbf{Answer:} 35.5 grams of \(\text{Na}_2\text{SO}_4\)

    \item How many moles of water are produced when 30 grams of hydrogen gas reacts with oxygen gas?
    \[
    2\text{H}_2 + \text{O}_2 \rightarrow 2\text{H}_2\text{O}
    \]
    \textbf{Answer:} 15 moles of \(\text{H}_2\text{O}\)

    \item Calculate the mass of magnesium oxide produced when 35 grams of magnesium reacts with oxygen gas.
    \[
    2\text{Mg} + \text{O}_2 \rightarrow 2\text{MgO}
    \]
    \textbf{Answer:} 58.3 grams of \(\text{MgO}\)

    \item Determine the number of moles of nitrogen dioxide produced when 40 grams of nitrogen reacts with oxygen gas.
    \[
    \text{N}_2 + 2\text{O}_2 \rightarrow 2\text{NO}_2
    \]
    \textbf{Answer:} 1.43 moles of \(\text{NO}_2\)

    \item How many grams of potassium chloride are produced when 45 grams of potassium reacts with chlorine gas?
    \[
    2\text{K} + \text{Cl}_2 \rightarrow 2\text{KCl}
    \]
    \textbf{Answer:} 86.6 grams of \(\text{KCl}\)

    \item Calculate the volume of carbon dioxide produced when 50 grams of propane combusts completely at STP.
    \[
    \text{C}_3\text{H}_8 + 5\text{O}_2 \rightarrow 3\text{CO}_2 + 4\text{H}_2\text{O}
    \]
    \textbf{Answer:} 67.2 liters of \(\text{CO}_2\)

    \item Determine the mass of aluminum oxide produced when 55 grams of aluminum reacts with oxygen gas.
    \[
    4\text{Al} + 3\text{O}_2 \rightarrow 2\text{Al}_2\text{O}_3
    \]
    \textbf{Answer:} 103.5 grams of \(\text{Al}_2\text{O}_3\)

    \item How many moles of sulfuric acid are produced when 60 grams of sulfur trioxide reacts with water?
    \[
    \text{SO}_3 + \text{H}_2\text{O} \rightarrow \text{H}_2\text{SO}_4
    \]
    \textbf{Answer:} 0.75 moles of \(\text{H}_2\text{SO}_4\)

    \item Calculate the mass of calcium sulfate produced when 65 grams of calcium hydroxide reacts with sulfuric acid.
    \[
    \text{Ca(OH)}_2 + \text{H}_2\text{SO}_4 \rightarrow \text{CaSO}_4 + 2\text{H}_2\text{O}
    \]
    \textbf{Answer:} 86.5 grams of \(\text{CaSO}_4\)
\end{enumerate}

\end{document}

