\documentclass{article}
\usepackage{amsmath}
\usepackage{chemfig}


\title{Stoichiometry Problems 2: Limiting Reactants}
\author{Answers}
\date{}


\begin{document}

\maketitle

\section*{Problems and Answers}

\begin{enumerate}
    \item If 5 grams of hydrogen gas (\(\text{H}_2\)) reacts with 20 grams of oxygen gas (\(\text{O}_2\)), which reactant is limiting, how many grams of water (\(\text{H}_2\text{O}\)) are produced, and how many grams of the excess reactant remain?
    \[
    2\text{H}_2 + \text{O}_2 \rightarrow 2\text{H}_2\text{O}
    \]
    \textbf{Answer:} Hydrogen is the limiting reactant. 45 grams of \(\text{H}_2\text{O}\) are produced. 16 grams of \(\text{O}_2\) remain.

    \item When 10 grams of aluminum (\(\text{Al}\)) reacts with 35 grams of chlorine gas (\(\text{Cl}_2\)), which reactant is limiting, how many grams of aluminum chloride (\(\text{AlCl}_3\)) are produced, and how many grams of the excess reactant remain?
    \[
    2\text{Al} + 3\text{Cl}_2 \rightarrow 2\text{AlCl}_3
    \]
    \textbf{Answer:} Aluminum is the limiting reactant. 49.4 grams of \(\text{AlCl}_3\) are produced. 20.1 grams of \(\text{Cl}_2\) remain.

    \item If 15 grams of methane (\(\text{CH}_4\)) reacts with 50 grams of oxygen gas (\(\text{O}_2\)), which reactant is limiting, how many grams of carbon dioxide (\(\text{CO}_2\)) are produced, and how many grams of the excess reactant remain?
    \[
    \text{CH}_4 + 2\text{O}_2 \rightarrow \text{CO}_2 + 2\text{H}_2\text{O}
    \]
    \textbf{Answer:} Methane is the limiting reactant. 41.3 grams of \(\text{CO}_2\) are produced. 35 grams of \(\text{O}_2\) remain.

    \item When 25 grams of iron (\(\text{Fe}\)) reacts with 30 grams of sulfur (\(\text{S}\)), which reactant is limiting, how many grams of iron(II) sulfide (\(\text{FeS}\)) are produced, and how many grams of the excess reactant remain?
    \[
    \text{Fe} + \text{S} \rightarrow \text{FeS}
    \]
    \textbf{Answer:} Iron is the limiting reactant. 39.9 grams of \(\text{FeS}\) are produced. 10 grams of \(\text{S}\) remain.

    \item If 50 grams of calcium carbonate (\(\text{CaCO}_3\)) reacts with 75 grams of hydrochloric acid (\(\text{HCl}\)), which reactant is limiting, how many grams of carbon dioxide (\(\text{CO}_2\)) are produced, and how many grams of the excess reactant remain?
    \[
    \text{CaCO}_3 + 2\text{HCl} \rightarrow \text{CaCl}_2 + \text{CO}_2 + \text{H}_2\text{O}
    \]
    \textbf{Answer:} Calcium carbonate is the limiting reactant. 22 grams of \(\text{CO}_2\) are produced. 36.5 grams of \(\text{HCl}\) remain.
\end{enumerate}

\end{document}

