
\documentclass{article}
\usepackage{amsmath}
\usepackage{chemfig}

\title{Stoichiometry Problems 3: Percent Yield}

\author{Richard Kiddle}
\date{}


\begin{document}

\maketitle

\section*{Problems}

\begin{enumerate}
    \item In a reaction, 10 grams of hydrogen gas (\(\text{H}_2\)) reacts with excess oxygen gas (\(\text{O}_2\)) to produce water (\(\text{H}_2\text{O}\)). If the actual yield of water is 80 grams, calculate the percent yield.
    \[
    2\text{H}_2 + \text{O}_2 \rightarrow 2\text{H}_2\text{O}
    \]
    \item When 15 grams of aluminum (\(\text{Al}\)) reacts with excess chlorine gas (\(\text{Cl}_2\)), 50 grams of aluminum chloride (\(\text{AlCl}_3\)) are produced. Calculate the percent yield.
    \[
    2\text{Al} + 3\text{Cl}_2 \rightarrow 2\text{AlCl}_3
    \]
    \item If 20 grams of methane (\(\text{CH}_4\)) reacts with excess oxygen gas (\(\text{O}_2\)), and the actual yield of carbon dioxide (\(\text{CO}_2\)) is 44 grams, calculate the percent yield.
    \[
    \text{CH}_4 + 2\text{O}_2 \rightarrow \text{CO}_2 + 2\text{H}_2\text{O}
    \]
    \item In a reaction, 25 grams of iron (\(\text{Fe}\)) reacts with excess sulfur (\(\text{S}\)) to produce iron(II) sulfide (\(\text{FeS}\)). If the actual yield of iron(II) sulfide is 40 grams, calculate the percent yield.
    \[
    \text{Fe} + \text{S} \rightarrow \text{FeS}
    \]
    \item When 30 grams of calcium carbonate (\(\text{CaCO}_3\)) reacts with excess hydrochloric acid (\(\text{HCl}\)), 22 grams of carbon dioxide (\(\text{CO}_2\)) are produced. Calculate the percent yield.
    \[
    \text{CaCO}_3 + 2\text{HCl} \rightarrow \text{CaCl}_2 + \text{CO}_2 + \text{H}_2\text{O}
    \]
\end{enumerate}

\section*{Real-Life Applications of Percent Yield}

\begin{enumerate}
    \item Explain how percent yield is important in the pharmaceutical industry when producing medications.
    \item Discuss the role of percent yield in the food industry, particularly in the production of processed foods.
    \item Describe how percent yield can impact the profitability of chemical manufacturing companies.
    \item Explain the significance of percent yield in environmental chemistry, especially in waste management and recycling processes.
    \item Discuss how percent yield is used in the development and optimization of new materials in materials science.
\end{enumerate}

\end{document}


